Supplement for Ward et al., 'Reduced diversity and increased specialization of Alaska salmon fishermen' 

### 2017-02-22 salmon/paper/salmon_paper_appendix_v3.Rmd
commit lost files

---
title: "Supplement for Ward et al., 'Reduced diversity and increased specialization of Alaska salmon fishermen...' "
author: ''
date: ''
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document: default
---

>>>>

---
title: "Supplement for Ward et al., 'Reduced diversity and increased specialization of Alaska salmon fishermen' "
author: ''
date: ''
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document: default
---
